Towards Transparency and Open Science

### 2023-01-11 manuscript.Rmd
add pdfpages

---
title: "Towards Transparency and Open Science"
subtitle: "A Principled Perspective on Computational Reproducibility and Preregistration"
output:
  bookdown::pdf_document2:
    latex_engine: "xelatex"
    toc: true
    number_sections: false
header-includes:
   - \usepackage{libertine}
fontsize: 12pt
geometry: "left=3.9cm, right=3.3cm, top=2.5cm, bottom=3cm"
papersize: a4
bibliography: references.bib
abstract: "`r paste0(c('\\\\noindent', readLines('abstract.md')), collapse = ' ')`"
csl: apa.csl
repro:
  files:
    - abstract.md
    - apa.csl
  tlmgr:
    - pgf
    - preview
    - libertine
  apt:
    - git
    - rsync
---

@@

>>>>

---
title: "Towards Transparency and Open Science"
subtitle: "A Principled Perspective on Computational Reproducibility and Preregistration"
output:
  bookdown::pdf_document2:
    latex_engine: "xelatex"
    toc: true
    number_sections: false
header-includes:
   - \usepackage{libertine}
   - \usepackage{pdfpages}
fontsize: 12pt
geometry: "left=3.9cm, right=3.3cm, top=2.5cm, bottom=3cm"
papersize: a4
bibliography: references.bib
abstract: "`r paste0(c('\\\\noindent', readLines('abstract.md')), collapse = ' ')`"
csl: apa.csl
repro:
  files:
    - abstract.md
    - apa.csl
  tlmgr:
    - pgf
    - preview
    - libertine
    - pdfpages
  apt:
    - git
    - rsync
---

@@

# Published Papers
